The Shape and Color of Politics

### 2023-10-12 chapter_2/src/slides/slides.qmd
updating the slides some more

---
title: "The Shape and Color of Politics"
author:
  - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
  revealjs:
    multiplex: true
    embed-resources: true
    theme: [dark, ../../assets/slides/custom.scss]
    transition: slide
    scrollable: true
    incremental: true
    slide-number: true
    toc: true
    toc-depth: 2
    slide-level: 5
    bibliography: ../../../assets/candidate_support_chapter_references.bib   
    self-contained: true
    output-file: color-book.html
execute:
  echo: false
  freeze: true
nocite: |
  @allaire_quarto_2022, @arel-bundock_marginaleffects_2022, @wickham_ggplot2_2016, @leeuw_jspsych_2015, @burkner_brms_2017,
---

@@

# Question guiding the project

Is color a source of political information that shapes the public's behaviors and attitudes?

@@

- Collect around 1,000 yard signs from House elections
  - 2016-2024
- Measuring the colors used on a yard sign:
  - Use a machine learning Python Library, `OpenCV` [@bradski_opencv_2000], that reads images and classifies their components.
    - Trained to classify each pixel in the image
    - Classifies it based on BGR value (reverse of RGB)
    - Looks for a range of values around the "Republican red" and "Democratic blue"

@@

::: {#fig-trial-1}

![Red condition](../study_1/assets/rep_yard_sign_round_1.png){#fig-red-1 width="6.5in"}

![Blue condition](../study_1/assets/dem_yard_sign_round_1.png){#fig-blue-1 width="6.5in"}

![White condition](../study_1/assets/cont_yard_sign_round_1.png){#fig-white-1 width="6.5in"}

@@

::: {#fig-trial-2}

![Red condition](../study_1/assets/rep_yard_sign_round_2.png){#fig-red-2 width=6.5in}

![Blue condition](../study_1/assets/dem_yard_sign_round_2.png){#fig-blue-2 width=6.5in}

![White condition](../study_1/assets/cont_yard_sign_round_2_3.png){#fig-white-2 width=6.5in}

@@

::: {#fig-trial-3}

![Red condition](../study_1/assets/rep_yard_sign_round_3.png){#fig-red-3 width=6.5in}

![Blue condition](../study_1/assets/dem_yard_sign_round_3.png){#fig-blue-3 width=6.5in}

![White condition](../study_1/assets/cont_yard_sign_round_2_3.png){#fig-white-3 width=6.5in}

@@

```{r}
#| label: fig-h-2-predictions-2
blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2"]][["blue_multinomial"]]
  , x_axis = "trial_1_blue_stimuli"
  , treatment = "Blue"
)
blue
```

>>>>

---
title: "The Shape and Color of Politics"
author:
  - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
  revealjs:
    multiplex: true
    embed-resources: true
    theme: [dark, ../../assets/slides/custom.scss]
    transition: slide
    scrollable: true
    incremental: false
    slide-number: true
    toc: false
    #toc-depth: 2
    slide-level: 5
    bibliography: ../../../assets/candidate_support_chapter_references.bib   
    self-contained: true
    output-file: color-book.html
execute:
  echo: false
  freeze: true
nocite: |
  @allaire_quarto_2022, @arel-bundock_marginaleffects_2022, @wickham_ggplot2_2016, @leeuw_jspsych_2015, @burkner_brms_2017,
---

@@

@@

- Collect around 1,000 yard signs from House elections
  - 2016-2022
- Measuring the colors used on a yard sign:
  - Use a machine learning Python Library, `OpenCV` [@bradski_opencv_2000], that reads images and classifies their components.
    - Trained to classify each pixel in the image
    - Classifies it based on BGR value (reverse of RGB)
    - Looks for a range of values around the "Republican red" and "Democratic blue"

@@

::: {.r-stack #fig-trial-1}

![Red condition](../study_1/assets/rep_yard_sign_round_1.png){.fragment #fig-red-1 width="6.5in"}

![Blue condition](../study_1/assets/dem_yard_sign_round_1.png){.fragment #fig-blue-1 width="6.5in"}

![White condition](../study_1/assets/cont_yard_sign_round_1.png){.fragment #fig-white-1 width="6.5in"}

@@

::: {.r-stack #fig-trial-2}

![Red condition](../study_1/assets/rep_yard_sign_round_2.png){.fragment #fig-red-2 width=6.5in}

![Blue condition](../study_1/assets/dem_yard_sign_round_2.png){.fragment #fig-blue-2 width=6.5in}

![White condition](../study_1/assets/cont_yard_sign_round_2_3.png){.fragment #fig-white-2 width=6.5in}

@@

::: {.stack #fig-trial-3}

![Red condition](../study_1/assets/rep_yard_sign_round_3.png){.fragment #fig-red-3 width=6.5in}

![Blue condition](../study_1/assets/dem_yard_sign_round_3.png){.fragment #fig-blue-3 width=6.5in}

![White condition](../study_1/assets/cont_yard_sign_round_2_3.png){.fragment #fig-white-3 width=6.5in}

@@

```{r}
#| label: fig-h-2-predictions-2
#| fig-cap: Blue yard signs = Democratic candidate
blue <- predicted_prob_bar(
  fitted_model = list_fitted[["h_2"]][["blue_multinomial"]]
  , x_axis = "trial_1_blue_stimuli"
  , treatment = "Blue"
)
blue
```
